Prediction of 2024 US election ...

### 2024-11-04 paper/paper.qmd
colin code update7

# Predict on the test data and check performance
predictions <- posterior_predict(bayesian_model_train, newdata = test_data)
```

>>>>

test_data_arizona = test_data[test_data$state == "Arizona", ]
# Predict on the test data and check performance
predictions <- posterior_predict(bayesian_model_train, newdata = test_data)
predictions_arizona = posterior_predict(bayesian_model_train, newdata = test_data_arizona)
```

```{r}
# Calculate the average predicted PCT for Harris
avg_predicted_pct_harris <- mean(predictions_arizona)

# Print the result
avg_predicted_pct_harris
